Generating Simulated Data

### 2021-03-12 docs/SimData.Rmd
weight diets part 1

@@

trueB_age_allbox <- NOBAom_ms$truebio_ss %>%
  #sum over polygons
  aggregate(dat$atoutput,list(dat$species,dat$agecl,dat$time, dat$prey),sum)

>>>>

source(here("simulated-data/config/NOBA2Config.R"))

@@

NOBAom_ms <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))

trueB_age_allbox <- NOBAom_ms$truebio_ss %>%
  #sum over polygons
  #aggregate(dat$atoutput,list(dat$species,dat$agecl,dat$time, dat$prey),sum)
  group_by(species,agecl,time) %>%
  summarise(sum(atoutput))
